---
title: "User Manual"
author: "User Manual"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# visualisationIMPACT

## Install package and load fonts

``` r
# Install development version from GitHub:

install.packages("devtools")
devtools::install_github("sharonorengo/visualisationIMPACT")

#Load fonts
install.packages("extrafont")
extrafont::loadfonts(device="win")  

```

## Pre-... before editing the plots
- orientation
- size output
- compile function to have the paranteers for barchart and boxplots

## For barcharts

### Simple barchart
``` r
# Install development version from GitHub:

install.packages("devtools")
devtools::install_github("sharonorengo/visualisationIMPACT")

#Load fonts
install.packages("extrafont")
extrafont::loadfonts(device="win")  

```

### Grouped barchart

```{r,eval =  F}
# Install development version from GitHub:

install.packages("devtools")
devtools::install_github("sharonorengo/visualisationIMPACT")

#Load fonts
install.packages("extrafont")
extrafont::loadfonts(device="win")  

```

## For boxplots

### Simple boxplot

``` r
# Install development version from GitHub:

install.packages("devtools")
devtools::install_github("sharonorengo/visualisationIMPACT")

#Load fonts
install.packages("extrafont")
extrafont::loadfonts(device="win")  

```
### Grouped boxplot

``` r
# Install development version from GitHub:

install.packages("devtools")
devtools::install_github("sharonorengo/visualisationIMPACT")

#Load fonts
install.packages("extrafont")
extrafont::loadfonts(device="win")  

```

## How to save ?



## How to personnalize the plot ? 

- add a title
- add a subtitle 
- see document ation ggplot can be overwrite 
- define other axis limits
- remove or add legend
- remove or add label
- hide axis


